% Created 2024-09-17 Tue 14:34
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
%\pagestyle{empty}
\usepackage[margin=1.9cm]{geometry}
\usepackage{gitinfo2}
\setcounter{secnumdepth}{0}
\author{Ramon Diaz-Uriarte}
\date{\today}
\title{Statistics part: what we will cover each day}
\date{\gitAuthorDate\ {\footnotesize (Release\gitRels: Rev: \gitAbbrevHash)}}
\hypersetup{
 pdfauthor={Ramon Diaz-Uriarte},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 30.0.60 (Org mode 9.7.5)},
 pdflang={English}}
\begin{document}

\maketitle
\section*{How to read this}
``Day 2'' refers to the second session or lesson of the classes devoted to stats. For example, that will most likely be 14-November-2025. (This notation allows us to reuse this file, even if we change the exact date of a lesson).


``Section 5'': refers to the section in the main PDF, ``R-basic-stats.pdf'', titled ``Basic statistics with R''. To be redundant, I often give in parentheses a short version of the section (e.g., ``section 5 (plots)'', where ``plots'' stands for ``Looking at the data: plots'' that is the full, long, section title of section number 5).

\subsection*{Speed}
\label{sec:speed}

% The plan below is not the ideal plan. % The ideal plan includes the ``omics'' slides and the categorical data analysis PDF.% , as well as a programming example of writing the code for a permutation test, which would be included at the end. And we want to go over what is an R package too.
Thus, I will try to go slightly faster than what is shown below, to allow time for discussion and to really cover all the material. This will be smoother if you read the notes before coming to class.


\section*{Day 1}
\label{sec:org21b08e0}
\begin{itemize}
  \item (I skip sections before 5 in class. That does not mean they are not relevant, just that they are very simple, and most likely already known by you.)
\item Sections: 5 (plots), 6 (two-sample t; including supplementary PDF about confidence intervals referred to in section 6.2), 7 (one and two-tailed), 8 (power)

  % \item For those interested, we will discuss \textbf{at the end of class (i.e., expect to stay after 19:00 on 11-November-2024)}, any doubts about the projects for the practical programming exercise.
\end{itemize}
\section*{Day 2}
\label{sec:org5a4c730}
\begin{itemize}
\item Whatever remains from Day 1. Sections: 9 (equiv. testing), 10 (bayesian), 11 (conf. int: see longer slides).
\end{itemize}
\section*{Day 3}
\label{sec:org609aabb}
\begin{itemize}
\item Paired stuff: 12.1, 12.2.1, 12.2.2, 12.2.3, 12.2.8, 12.3, 12.4, 12.5 (plots for paired), 12.6, 13 (one-sample), 14 (non-par), 15 (non-indep data), 16 (symmetry and paired t). 12.7 (a first taste of lin.mods. ---only if time). Start section 18. \textbf{Read the external files (e.g., CI-p-value-examples.pdf) on your own BEFORE class, I will answer questions about them, but I won't go over them in class.}
\end{itemize}
\section*{Day 4 }
\label{sec:org394fbf9}
\begin{itemize}
\item Whatever remains from Day 3: Section 18, including the two external files (anova basic theory and anova theory even simpler); section 19 (FWER and FDR), some 20 (two-way anova). % \textbf{Look at the notes for section 20 BEFORE class}.

   \textbf{Unless} you look at the notes \textbf{before you come to class} this material \textbf{will not make any sense}. The two-way anova section is long (more than 50 pages), possibly completely new, and possibly not intuitive nor easy.

\end{itemize}
\section*{Day 5 }
\label{sec:orgcb0a12f}
\begin{itemize}
\item sections: 20 (two-way anova), 21 (regression).


  Again, do not expect to understand this starting from 0 in just two hours of class. Come to class having looked at the material, \textbf{even if during the on your own, before-class, reading it seems confusing}.

\end{itemize}
\section*{Day 6 }
\label{sec:org6f322e8}
\begin{itemize}
\item Sections 22 (multiple regression), 23 (ancova), 24 (interactions, summary)
\end{itemize}
\section*{Day 7 }
\label{sec:org2142285}
\begin{itemize}
\item Sections 25 (diagnostics), 26 (variable/model selection), 28 (experimental design)
\end{itemize}
\section*{Day 8 }
\label{sec:org3d49cf0}
\begin{itemize}
\item Section 29 (causal inference: see additional PDF --- \textbf{really read the additional PDF on your own before coming to class}; otherwise, this will make no sense in just the time we have in class).
\end{itemize}
\section*{Day 9}
\begin{itemize}
\item Section 30 (ratios)
\item Categorical data analysis
\end{itemize}

\section*{Day 10}
\begin{itemize}
\item Omics slides
\item Miscellaneous doubts about stats.
\item Miscellaneous doubts about the assignment.
\item Any possible major lingering issues about the R part (e.g., R packages)
\end{itemize}



\label{sec:org32ab79d}

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
